\begin{thebibliography}{13}
    \bibitem{toan_roi_rac} 
    Nguyễn Đức Nghĩa, Nguyễn Tô Thành, 
    \textit{Toán rời rạc},
    NXB Đại học Quốc gia Hà Nội, 2009.
    
    \bibitem{lap_trinh_tien_hoa} 
    Nguyễn Đình Thúc,
    \textit{Lập trình tiến hóa},
    NXB Giáo dục, 2009.

    \bibitem{xin_yao_paper} 
    Bo Yuan, Huanhuan Chen, Xin Yao,
    \textit{ptimal Relay Placement for Lifetime Maximization in Wireless Underground Sensor Networks},
    Information Sciences, Volume 418-419, December 2017, Pages 463-479.

    \bibitem{edgar_paper} 
    Edgar H.Callaway Jr.,
    \textit{Wireless Sensor Networks: Architectures and Protocols},
    A CRC Press Company, 2004.

    \bibitem{anna_paper} 
    Anna Ha’c,
    \textit{Wireless Sensor Network Designs},
    University of Hawaii at Manoa, Honolulu, USA, John Wiley \& Sons Ltd, 2003.

    \bibitem{dietrich_paper} 
    Isabel Dietrich, Falko Dressler,
    \textit{On the Lifetime of Wireless Sensor Networks},
    Dept. of Computer Science 7, University of Erlangen, Martensstr. 3, 91058 Erlangen, Germany.

    \bibitem{convex_optimization} 
    Stephen Boyd, Lieven Vandenberghe,
    \textit{Convex Optimization},
    Cambridge university press, 2004.

    \bibitem{gtvlt} 
    Lê Minh Hoàng,
    \textit{Giải thuật và Lập trình},
    NXB Đại học Sư phạm Hà Nội, 2005.

    \bibitem{thomas_paper} 
    Thomas H. Cormen, Charles E. Leiserson, Ronald L. Rivest, and Clifford Stein,
    \textit{Introduction to Algorithms, Second Edition},
    MIT Press and McGraw-Hill, 2001. ISBN 0262032937. Section 26.2: The Ford-Fulkerson method, pp. 651–664.

    \bibitem{Giridhar} 
    Giridhar, A. and Kumar, P. 2005,
    \textit{Maximizing the Functional Lifetime of Sensor Networks},
    In 4th International Symposium on Information Processing in Sensor Networks (IPSN 2005), Los Angeles, CA.

    \bibitem{Yu2001} 
    Yu, Y., Govindan, R., and Estrin, D. 2001,
    \textit{Geographical and Energy Aware Routing: a recursive data dissemination protocol for wireless sensor networks},
    Technical Report UCLA/CSD-TR-01-0023, UCLA Computer Science Department.

    \bibitem{Wang2003} 
    Wang, X., Xing, G., Zhang, Y., Lu, C., Pless, R., and Gill, C. 2003,
    \textit{Integrated coverage and connectivity configuration in wireless sensor networks},
    In 1st ACM Conference on Embedded Networked Sensor Systems (ACM SenSys 2003). Los Angeles, CA, 28–39.

    \bibitem{Baydere2005} 
    Baydere, S., Safkan, Y., and Durmaz, O. 2005,
    \textit{Lifetime Analysis of Reliable Wireless Sensor Networks},
    IEICE Transactions on Communications E88-B, 6, 2465–2472.
\end{thebibliography}
